\EVOSUITE at the SBST 2020 Tool Competition

### 2020-03-25 papers/sbst20/main.tex
Spoon results are in another zip file.

\subsubsection*{GUAVA-212, GUAVA-22, PDFBOX-265, PDFBOX-278, PDFBOX-285,
PDFBOX-40, PDFBOX-91, PDFBOX-62} The mutation analysis failed due to a
\texttt{java.util.concurrent.ExecutionException} thrown by the experimental
infrastructure.

%% PDFBOX-235 0% coverage 0% mutation score

\subsubsection*{PDFBOX-235} \EVOSUITE crashed due to some Mocking stuff.

%% SPOON

\subsubsection*{SPOON} There is no \texttt{logs.log} file to check \EVOSUITE's
log messages.  There is any test suite for any SPOON
class.  The reason might be due to
\texttt{java.io.IOException: Not a valid directory name: /var/benchmarks/projects/spoon-core-7.2.0/src/main/java}.
in the \texttt{log\_detailed.txt} file.  Also, all \texttt{transcript.csv} are
empty.  Thus, it seems the experimental infrastructure do not even attempt to
generate test cases for any SPOON class.  Question: how did \EVOSUITE achieved
a 72.5\% coverage for, e.g., SPOON-253 if there is no test suite or even a valid
attempt?

>>>>

\subsubsection*{GUAVA-212, GUAVA-22, PDFBOX-265, PDFBOX-278, PDFBOX-285,
PDFBOX-40, PDFBOX-91, PDFBOX-62, SPOON-105, SPOON-253} The mutation analysis
failed due to a \texttt{java.util.concurrent.ExecutionException} thrown by the
experimental infrastructure.

%% PDFBOX-235 0% coverage 0% mutation score
%% SPOON-155 0% coverage 0% mutation score

\subsubsection*{PDFBOX-235, SPOON-105} \EVOSUITE crashed due to some Mocking stuff.
